### 2012-06-03 3.tex
Chapter 2 draft done.

\chapter{Static and derived phonotactic constraints in Turkish} 
\label{turkish}

%This chapter attempts to derive which phonotactic judgemetns are internalized by

@@

\begin{example}
Backness harmony wordlikeness forced choices \citep[314]{Zimmer1969}:

\vspace{0.5\baselineskip}
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pemez & 30                   & pemaz & 2  \\
tipez & 24                   & tipaz & 8  \\ 
terüz & 19                   & teruz & 13 \\ % roundness violator
teriz & 28                   & terız & 3  \\
tokaz & 26                   & tokez & 6  \\ % roundness violator
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}
Roundness harmony forced choice wordlikeness judgements:

\vspace{0.5\baselineskip}
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pörüz & 32 & pöriz & 0  \\
tatız & 20 & tatuz & 12 \\
tüpüz & 31 & tüpiz & 1  \\
takız & 22 & takuz & 10 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}
Labial attraction wordlikeness forced choices \citep[314]{Zimmer1969}:

\vspace{0.5\baselineskip}
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{aPu} & \multicolumn{2}{l}{aPı} \\
\midrule
pamuz & 17              & pamız & 15 \\
tafuz & 21              & tafız & 11 \\
tapuz & 17              & tapız & 15 \\
mavuz & 16              & mavız & 16 \\
tabuz & 16              & tabız & 16 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}
Arabic verbs of coming into being: \\
\begin{tabular}{l l l l}
kabiːr  & `big'        & kabura  & `become big'       \\
ħasan   & `handsome'   & ħasuna  & `become beautiful' \\
dʒadiːb & `barren'     & dʒaduba & `become dry'       \\
\end{tabular}
%b. & saʁiir & }`become small'     & (cf. \emph{saʁiːr} `small') \\
\end{example}

@@

\begin{example}
\textsc{Labial harmony} and etymology in TELL \citep[][187]{Inkelas2001}:

\vspace{0.5\baselineskip}
\begin{tabular}{l r r r}
        & aPu & aPı & $p$-value \\
Native  & 12  & 11  & \multirow{2}{*}{0.042} \\
Foreign & 84  & 28  \\
\end{tabular}
\end{example}

>>>>

%\chapter{Static and derived phonotactic constraints in Turkish} 
\label{turkish}

@@

\begin{example}[Backness harmony wordlikeness forced choices (\citealp{Zimmer1967}:314)]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pemez & 30                   & pemaz & 2  \\
tipez & 24                   & tipaz & 8  \\ 
terüz & 19                   & teruz & 13 \\ % roundness violator
teriz & 28                   & terız & 3  \\
tokaz & 26                   & tokez & 6  \\ % roundness violator
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons, roundness harmony]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pörüz & 32 & pöriz & 0  \\
tatız & 20 & tatuz & 12 \\
tüpüz & 31 & tüpiz & 1  \\
takız & 22 & takuz & 10 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{aPu} & \multicolumn{2}{l}{aPı} \\
\midrule
pamuz & 17              & pamız & 15 \\
tafuz & 21              & tafız & 11 \\
tapuz & 17              & tapız & 15 \\
mavuz & 16              & mavız & 16 \\
tabuz & 16              & tabız & 16 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Arabic stative verbs]
\begin{tabular}{l l l l}
kabiːr  & `big'        & kabura  & `become big'       \\
ħasan   & `handsome'   & ħasuna  & `become beautiful' \\
dʒadiːb & `barren'     & dʒaduba & `become dry'       \\
\end{tabular}
%b. & saʁiir & }`become small'     & (cf. \emph{saʁiːr} `small') \\
\end{example}

@@

\begin{example}[\textsc{Labial harmony} and etymology in TELL \citealp{Inkelas2001}:187]
\begin{tabular}{l r r r}
        & aPu & aPı & $p$-value \\
Native  & 12  & 11  & \multirow{2}{*}{0.042} \\
Foreign & 84  & 28  \\
\end{tabular}
\end{example}
